The pollination trade-off

### 2018-11-13 paper/manuscript.Rmd
Separate awknoledgements

We thank  Cátedra de Botánica General, Facultad de Agronomía, Universidad de Buenos Aires. 
The Agrasar and Bordeu families, and the University of Buenos Aires, for logistical support and permission to conduct this study at estancias Anquilóo, Las Chilcas and San Claudio, respectively. 
Field work was supported by grants PICT 08–12504 and 0851. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
DBS and JMT acknowledge the support of a Rutherford Discovery Fellowship. 
DBS also awknoledges the Marsden Fund Council from New Zealand Government funding.

>>>>

`r paste(drake::readd(acknowledgements), collapse = "")`
